The Concurrent Calculi Formalisation Benchmark

### 2024-04-18 short-paper/short-paper.tex
removed duplication

Much current research on concurrent calculi includes aspects that are
not covered by our benchmark challenges, for example constructs such as
choice constructs and recursion.
%  Features that are in wide
% use, but not covered by our benchmark, include choice constructs and
% recursion. 
Some interesting research topics that build on the
fundamental aspects in our benchmark include multiparty session
types~\cite{10.1145/2827695}, choreographies~\cite{Carbone2013},
higher-order calculi~\cite{Hirsch2022}, conversation
types~\cite{DBLP:journals/tcs/CairesV10}, psi-calculi~\cite{lmcs:696},
and encodings between different
calculi~\cite{DBLP:journals/iandc/Gorla10,DBLP:journals/iandc/DardhaGS17}.
The meta-theory of these topics includes aspects---\eg well-formedness conditions on
global types, partiality of end-point projection functions,
\etc---that we do not address.

>>>>

Much current research on concurrent calculi includes aspects that are
not covered by our benchmark challenges, for example constructs such as
choice and recursion.
%  Features that are in wide
% use, but not covered by our benchmark, include choice constructs and
% recursion. 
Some interesting research topics that build on the
fundamental aspects in our benchmark include multiparty session
types~\cite{10.1145/2827695}, choreographies~\cite{Carbone2013},
higher-order calculi~\cite{Hirsch2022}, conversation
types~\cite{DBLP:journals/tcs/CairesV10}, psi-calculi~\cite{lmcs:696},
and encodings between different
calculi~\cite{DBLP:journals/iandc/Gorla10,DBLP:journals/iandc/DardhaGS17}.
The meta-theory of these topics includes aspects---\eg well-formedness conditions on
global types, partiality of end-point projection functions,
\etc---that we do not address.
